On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-01 docs/mvfits_paper/mvf.tex
adding citations for stepwise

To consider these two approaches in a largely automated way (i.e. where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.

@@

\par A well known method for finding an approximate solution to this problem is the so-called ``greedy'' algorithm:

>>>>

To consider these two approaches in a largely automated way (i.e. where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf, GVK022791892, 1978AnSta, Pandit84}.

@@

\par A well known method for finding an approximate solution to this problem is the so-called ``greedy'' algorithm (e.g. \cite{Field:2011mf, GVK022791892}):
